### 2022-07-26 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@01b0bf77e27b1d7dd71250d44c5b322979bd64c1 🚀

%
\href{https://orcid.org/0000-0003-2791-8383}{Gracielle\,T. Higino}%
%
\,\textsuperscript{1,2,‡}\quad %
\href{https://orcid.org/0000-0001-5030-3470}{Fredric\,M. Windsor}%
%
\,\textsuperscript{3,‡}\quad %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{4,5,6,‡}\quad %
\href{https://orcid.org/0000-0002-2212-3584}{Gabriel\,Dansereau}%
%
\,\textsuperscript{4,6,‡}\quad %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{4,6,‡}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{4,6,‡}

\textsuperscript{1}\,The University of British
Columbia\quad \textsuperscript{2}\,Computational Biodiversity Science
and Services\quad \textsuperscript{3}\,School of Natural and
Environmental Sciences, Newcastle
University\quad \textsuperscript{4}\,Université de
Montréal\quad \textsuperscript{5}\,Université de
Sherbrooke\quad \textsuperscript{6}\,Quebec Centre for Biodiversity
Science

\textsuperscript{‡}\,These authors contributed equally to the work\\

>>>>

%
\href{https://orcid.org/0000-0003-2791-8383}{Gracielle\,T. Higino}%
%
\,\textsuperscript{1}\quad %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{2,3,4}\quad %
\href{https://orcid.org/0000-0002-2212-3584}{Gabriel\,Dansereau}%
%
\,\textsuperscript{2,4}\quad %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{2,4}\quad %
\href{https://orcid.org/0000-0001-5030-3470}{Fredric\,M. Windsor}%
%
\,\textsuperscript{5}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{2,4}

\textsuperscript{1}\,Biodiversity Research Centre, University of British
Columbia\quad \textsuperscript{2}\,Université de
Montréal\quad \textsuperscript{3}\,Université de
Sherbrooke\quad \textsuperscript{4}\,Quebec Centre for Biodiversity
Science\quad \textsuperscript{5}\,School of Natural and Environmental
Sciences, Newcastle University

### 2022-07-26 preprint.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@01b0bf77e27b1d7dd71250d44c5b322979bd64c1 🚀

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0003-2791-8383}{Gracielle\,T. Higino}%
%
\,\textsuperscript{1,2,‡}, %
\href{https://orcid.org/0000-0001-5030-3470}{Fredric\,M. Windsor}%
%
\,\textsuperscript{3,‡}, %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{4,5,6,‡}, %
\href{https://orcid.org/0000-0002-2212-3584}{Gabriel\,Dansereau}%
%
\,\textsuperscript{4,6,‡}, %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{4,6,‡}, %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{4,6,‡}
\vskip 1em
\textsuperscript{1}\,The University of British
Columbia; \textsuperscript{2}\,Computational Biodiversity Science and
Services; \textsuperscript{3}\,School of Natural and Environmental
Sciences, Newcastle University; \textsuperscript{4}\,Université de
Montréal; \textsuperscript{5}\,Université de
Sherbrooke; \textsuperscript{6}\,Quebec Centre for Biodiversity
Science\\
\textsuperscript{‡}\,These authors contributed equally to the work\\
\vskip 1em
\textbf{Correspondance to:}\\
Gracielle T. Higino --- \texttt{graciellehigino@gmail.com}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
}
\end{flushleft}

>>>>

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0003-2791-8383}{Gracielle\,T. Higino}%
%
\,\textsuperscript{1}, %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{2,3,4}, %
\href{https://orcid.org/0000-0002-2212-3584}{Gabriel\,Dansereau}%
%
\,\textsuperscript{2,4}, %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{2,4}, %
\href{https://orcid.org/0000-0001-5030-3470}{Fredric\,M. Windsor}%
%
\,\textsuperscript{5}, %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{2,4}
\vskip 1em
\textsuperscript{1}\,Biodiversity Research Centre, University of British
Columbia; \textsuperscript{2}\,Université de
Montréal; \textsuperscript{3}\,Université de
Sherbrooke; \textsuperscript{4}\,Quebec Centre for Biodiversity
Science; \textsuperscript{5}\,School of Natural and Environmental
Sciences, Newcastle University\\
\vskip 1em
\textbf{Correspondance to:}\\
Gracielle T. Higino --- \texttt{graciellehigino@gmail.com}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
}
\end{flushleft}
